### 2016-03-05 AcademicPaperSummaries/PaperSummaries.tex
added week nine content

\underline{Week 9}
\end{document}

>>>>

\underline{Week 9}

\textbf{Crenshaw, Martha. 2007. “Explaining Suicide Terrorism: A Review Essay.” Security Studies Vol. 16 no. 1, p. 133-162.}

\underline{Keywords} review essay;

\underline{Research question and research area} Crenshaw provides a review of the use of suicide terrorism, and what reserachers have found to be important determinants. She is primarily focused on the degree to which existing studies of suicide terrorism and  highlights the lack of methodological and definitional coherence.\\
\underline{Summary of argument and mechanism} This is a survey article, so there is no real theory being proposed.\\
\underline{Data \& methods} ``Data'' are thirteen existing articles about the use of suicide terrorism \\
\underline{Findings} Crenshaw is not impressed. However, she is insightful about gaps in research design and in identifying how articles fit together, and how their underlying assumptions compare to each other.\\
\underline{Notes on related papers}\\

\textbf{Pape, Robert A. 2003. “The Strategic Logic of Suicide Terrorism.” American Political Science Review Vol. 97, No. 3.}
Keywords: suicide terrorism, descriptive statistics

\underline{Research question and research area} Pape is intereted in why groups use suicide terrorism and argues that the tactic is a sucessful way to coerce liberal democracies to provide terroritial concessions. Pape defines suicide terrorism as being an attack carried out in such a way that the attacker does not expect to survive the mission.  As Crenshaw points out, this is a fuzzy (and vauge) definition.\\
\underline{Summary of argument and mechanism} Suicide terrorism is a ``strategy of coercion'' that is successful by inflicting enough pain on the target so as to compel the government to change.\\
\underline{Operative definition of terrorism} Pape divides terrorism into ``demonstrative'', ``destructive'' and ``suicide terrorism.'' The first is intended to generate an audience for the group, the second to coerce opponents and mobilize support, and the third (``the most aggressive form of terrorism'') values coercion over the group's constituents. Note that throughout the paper, Pape has an underlying model of suicide terrorism in which the tactic is negatively responded to by the group's supporters and that supporters view such attacks as wasteful of life. I think that this is a naieve perspective. \\
\underline{Data \& methods} Pape uses ``suicide campaigns'' as his dependent variable. He records 188 suicide terror attacks between 1980-2001, which he clusters into 16 ``campaigns'' that have been organized by terrorists into coherent strategic blocks. This is a controversial sorting. He also has a mini-case study on Hamas.\\
\underline{Findings} Using suicide terrorism is positively correlated with government concessions; sucidie terrorism is a rational strategy.\\
\underline{Notes on related papers} We savaged this paper in class, and there is a lot of dodgy content in the theory and empirics. However, it is worth noting that the heirarchy of types of terrorism, in escalating level of destructiveness, is actually a decently subtle conceptual point that many of the theorists of terrroism have had a hard time with.\\

\textbf{Ashworth, Scott, Johsua D. Clinton, Adam Meirowitz, and Kristopher W. Ramsay. 2008. “Design, Inference, and the Strategic Logic of Suicide Terrorism.” American Political Science Review Volume 102 (2): 269-273;  Pape, Robert A. 2008. “Methods and Findings in the Study of Suicide Terrorism.” American Political Science Review Volume 102 (2): 275-277;) Ashworth, Scott, Johsua D. Clinton, Adam Meirowitz, and Kristopher W. Ramsay. 2008. “Design, Inference, and the Strategic Logic of Suicide Terrorism: A Rejoinder.” Available at http://www.princeton.edu/~clinton/WorkingPapers/ACMRResponse.pdf}

Methodological spat about the selection of observations in Pape's study of suicide terrorism and particularly whether he selected for the dependent variable. If you're into that kind of thing. Jordan did these summaries for class. I'm scraping them because they're good!

Ashworth et al. (2008a)
\underline{Key point} By only looking at instances of suicide terror, Pape samples on the dependent variable.
This means that he can’t shed light on why suicide terror happens, since he doesn’t compare the cases where it occurs to the cases where it does not. While he can speak to the probability of an occupation given suicide terror, he cannot speak to the probability of suicide terror given an occupation. You also can’t “reverse engineer” this through Bayes’ Rule since Pape’s data doesn’t inform you of the probability of an occupation given no suicide terror, which you’d need the denominator. Once Ashworth et al. account for the uncertainty this leads to in Pape’s estimates, we see that Pape’s study can tell us almost nothing about the probability of suicide terror conditional on foreign occupation.

Pape's response is pretty lame: boils down to ``read my book!'' The exachange devolves from there.\\

\textbf{Pedahzur, Ami and Arie Perliger. 2006. “The Changing Nature of Suicide Attacks - A Social Network Perspective.” Social Forces 84 (4): 1987-2008.}

Keywords: social networks; terrorism\\

\underline{Research question and research area} Pedahzur and Perlinger want to know how people become radicalized into becoming suicide bombers and take a social network approach. They are one of the few in the suicide bombing literature that really push the divergence in motivation and goals between leaders and foot soldiers/fighters.\\
\underline{Summary of argument and mechanism} Arguement is that suicide bombers are recruited by diffuse networks of personal associates rather than in a top-down process.\\
\underline{Data \& methods} Map a social network of Palestinian suicide bombers from open-source information, including press releases, organization websites, and news articles. Created three levels of ties: family ties, long-term friendships, and acquantances.\\
\underline{Findings} One of their weirdest findings is that recruitment networks of sucicide bombers crosses organizations (with the same networks producing suicide bombers for more than one group.) They also find that suicide bombers are peripheral to their networks, and thus conclude that ``suicide bombers are not recruited nor do they undergo a training process.'' Unclear how they generate these conclusions from their data. \\
\underline{Notes} The connection between theory and methods are somewhat incoherent in this paper, but there are some observations about group structure in the introduction tha are worth keeping. I think that they are somewhat blase about the skills needed to create a diffuse bombing campaign--but others with experience in these things are more convinced. \\

\textbf{Wade, Sara Jackson and Dan Reiter. 2007. “Does Democracy Matter?: Regime Type and Suicide Terrorism.” Journal of Conflict Resolution Vol. 51, No. 2, 329-348.}

\end{document}
